\documentclass[a4paper]{MagicalCV}

% Removing page numbers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\onehalfspacing

% Change the geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Defining your colors
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% start document
\begin{document}

% Last update time
\lastupdated

% Title name
\namesection{}{Daniil Selivanov}

% Column one
\begin{minipage}[t]{0.33\textwidth} 

% About
\cvsection{About} 

Python Developer with experience in \\DevOps.

Passionate about automating processes and writing readable code.

For more details, refer to my \\LinkedIn profile.
\sectionsep

% Links
\cvsection{Links}\\
\location{Tbilisi, Georgia}

\telegram{\href{https://t.me/layz7}{@layz7}}

\email{\href{mailto:d.y.selivanov@icloud.com}{d.y.selivanov@icloud.com}}

\linkedin{\underline{\href{https://www.linkedin.com/in/daniil-selivanov-ba338b1b7/}{Daniil Selivanov}}}
\sectionsep

% Skills
\cvsection{Skills}

\subsection{Programming}
Python

\subsection{Data Engineering}
Apache Airflow \textbullet{} 
ETL \textbullet{} 
SQL (PostgreSQL) \textbullet{} 
ORM (SQLAlchemy)

\subsection{Web Technologies}
Selenium \textbullet{} 
Scrapy

\subsection{API integrations}
Telegram \textbullet{} 
GitLab \textbullet{} 
JIRA

\subsection{CI/CD \& DevOps}
GitLab-CI \textbullet{} 
Linux \textbullet{} 
Docker
\sectionsep

% Perks
\cvsection{Perks}

Team Work \textbullet{}
Annotation, documentation and code commenting \textbullet{}
Building adaptive microservices \textbullet{}
Dev-tools implementation \textbullet{}
Critical thinking
\sectionsep

% Education
\cvsection{Education} 

\subsection{Tomsk State University of \\ Control Systems and \\ Radioelectronics}
\descript{Specialist in Information Security of Automated (Banking) Systems}
\cvevent{2015 -- 2020}{Tomsk, RU} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\sectionsep

% Languages
\cvsection{Languages}

\textbf{Russian:} Native \\
\textbf{English:} B1 (Working Proficiency)
\sectionsep

% Column two
\end{minipage} 
\hfill
\begin{minipage}[t]{0.64\textwidth} 

% Experience
\cvsection{Experience}

\runsubsection{Python Backend Developer} \\
\descript{SecurityGen}
\cvevent{Feb 2022 – Present}{Saint Petersburg, RU -> Tbilisi, GE} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\textbf{Products ensuring information security in the telecommunications industry:}
\begin{tightemize}
  \item Implemented a licensing mechanism for products.
  \item Optimized data filtering processes.
  \item Created a tool that recovers data from log files and uploads it into the database.
  \item Created data schemas and validators.
  \item Managed project dependencies.
  \item Implemented new endpoints for the project.
  \item Legacy code support and optimization.  
\end{tightemize}

\textbf{Stack:}
\begin{tightemize}
  \item \textbf{Python, Asyncio, Aiohttp, Celery}
  \item \textbf{Marshmallow, Json Schema}
  \item \textbf{PostgreSQL, SQLAlchemy, Alembic}
\end{tightemize}
\sectionsep

\runsubsection{Python Developer / DevOps Engineer} \\
\descript{Positive Technologies}
\cvevent{Jul 2019 – Feb 2022}{Tomsk, RU -> Saint Petersburg, RU} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space


\textbf{Product for gathering and analyzing vulnerabilities from vendor websites:}

\begin{tightemize}
  \item Led project releases, contributed to architecture development, managed infrastructure deployment, and oversaw release cycle management.
  \item Conducted code reviews for project contributors.
  \item Optimized data processing pipelines.
  \item Configured Celery workers.
  \item Provided DevOps support for the project.  
\end{tightemize}

\textbf{Security Vulnerability Scanner:}
\begin{tightemize}
  \item Developed scripts for CIS-compliant audit and compliance checks.
  \item Legacy code maintenance, refactoring, and optimization.
  \item Mentored and onboarded new team members.
  \item Deployed target stands for scanning and testing.
\end{tightemize}

\textbf{Stack:}
\begin{tightemize}
  \item \textbf{Python, Apache Airflow, Celery}
  \item \textbf{Gitlab-CI, Docker}
  \item \textbf{Scrapy, Selenium}
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}
